---
title: Solutions
font : 12pt
geometry: margin=1.2in
header-includes:
    - \usepackage{setspace}
    - \setstretch{1,2}
    - \usepackage{times}
# Rscript --no-init-file -e 'rmarkdown::render("Solutions.Rmd", output_format = "pdf_document")'
---


# Practice 1

```{r setup, echo = FALSE}
library(graphicsutils)
myblue <- "#7eb6d6"
myred <- "#e080a3"
mygreen <- "#d4e09b"
mygrey <- "grey35"
mypar <- list(fg=mygrey, col.lab=mygrey, col.axis=mygrey, bg="transparent", las = 1, cex.main=2, cex.axis=1.4, cex.lab=1.4, bty="l")
```


## $P(A \cup B \cup C)$

<!-- Faire une figure -->

$$P(A \cup B \cup C) = P(A \cup B) + P(C) - P(A \cup B \cap C)$$

$$P(A \cup B \cup C) = P(A) + P(B) - P(A \cap B)  + P(C) - P(A \cup B \cap C)$$

$$P(A \cup B \cup C) = P(A) + P(B) - P(A \cap B)  + P(C) - P(A \cap C) - P(A \cap B) + P(A \cap B \cap C)$$





# Solution 2

X = "ducks killed" ; $\Omega$ = {0,1,2,3}

1. (1,1,0) (1,0,1) (0,1,1); $P(X = 2) = 3*p^2*(1-p)$

Event (0,0,1); X = "number of failure before first success"

2. (0,0,1) ; $P(X = 2) = (1-p)^2p$

3. Here it is:

$$P(X = k) = \binom{n}{k} p^k(1-p)^{n-k}$$

4. Here it is:

$$P(X = k) = p(1-p)^{n-1}$$





# Practice 3

## Model

1- Dave: N(0,1)

2- Amael: N(.5,3)

3- Will: N(.5,.5)

<!-- insert figure -->

```{r normal, echo=FALSE, fig.width=7, fig.height=4.5}
seqx <- seq(-6,6,0.1)
par(mypar)
plot(seqx, dnorm(seqx, .5, .5), type="n")
lines(seqx, dnorm(seqx), type="l", col=myblue, lwd=2)
lines(seqx, dnorm(seqx, .5, 3), col=mygreen, lwd=2)
lines(seqx, dnorm(seqx, .5, .5), col=myred, lwd=2)
legend("topleft", legend = c("Dave", " Amael",  "Will"), col=c(myblue, mygreen, myred), lwd=3, bty="n")
```


## Starting on time

$$P("all there before 0") = P(X_1<0)P(X_2<0)P(X_3<0)$$



## Start delayed by at least half an hour

$$P("at least one 30min late") = 1-P("all there before")$$

$$P("at least one 30min late") = 1-P(X_1<.5)P(X_2<.5)P(X_3<.5)$$



## Starting the meeting

ontime / avec .5 min de retard / à quelle heure commencera

when all three are present

"start time x" = "all there at x" = "the last arrive at x the two other where there"

Z =

$P(X_1<x)P(X_2<x)f_3(x) + P(X_1<x)P(X_3<x)f_2(x) + P(X_2<x)P(X_3<x)f_1(x)$=



## Solution 4

60\$ = 20*3\$

$$E(X) < 20$$

$$\frac{1-p}{p} < 20$$

$$p < \frac{1}{21}$$


## Solution 5

2 random variables:

- X = 1 ("sick"); X = 0 ("sane")

- T = 1 ("test positive"); T = 0 ("test negative")


We know $P(X=1)$ (external study "prior", we'll use it as the parameter of a binomial variable)

In 1. we need to determine $P(X=1|T=1)$

$$P(X=1|T=1) = \frac{P(X=1 \cap T=1)}{P(T=1)}$$

$$P(X=1|T=1) = \frac{P(T=1|X=1)P(X=1)}{P(T=1|X=1)P(X=1)+P(T=1|X=0)P(X=0)}$$

$$P(X=1|T=1) = \frac{1}{1+\frac{P(T=1|X=0)P(X=0)}{P(T=1|X=1)P(X=1)}}$$

$$P(X=1|T=1) = \frac{1}{1+\frac{\alpha(1-\pi)}{(1-\alpha)\pi}}$$


For 2. determine $P(X=1|T=0)$

$$P(X=1|T=0) = \frac{P(X=1 \cap T=0)}{P(T=0)}$$

$$P(X=1|T=0) = \frac{1}{1+\frac{P(T=0|X=0)P(X=0)}{P(T=0|X=1)P(X=1)}}$$

$$P(X=1|T=0) = \frac{1}{1+\frac{(1-\beta)(1-\pi)}{\beta\pi}}$$


## Practice 6


<!-- $$B = Nt(\beta_{2,3}, \beta_{1,3}, \beta_{1,2})$$

$$\Phi(k) = \sum_i\sum_j \alpha_{i,j} m_{k+1,i} x_j + \sum_{l} \beta_{k+1,l}$$

$$logit(P(X=S_k)) = \mathcal{N}(\Phi(k), \sigma)$$ -->


## Practice 7
